---
title: "Mass Shootings in the USA"
author: "Hannah Reitz & Sophie Hensgen"
date: "5/14/2020"
output: html_document
---

```{r}
library(openxlsx)
library(xml2)
library(rvest)
library(jsonlite)
library(robotstxt)
library(RSocrata)
library(dplyr)
library(rlist)
library(pipeR)
library(gtrendsR)
library(lubridate)

```
## Theory and Hypotheses

More dead people --> more media attention --> higher attention in Google trends

newworthiness in den Medien

1. The more people got injured, the longer the shooting stayed in the trends.

2. The more deaths, the longer the shooting stayed in the trends.

evtl. newswothiness in Kombination mit inequality

3. If the shooter is black, the shooting stayed longer
in the trends.

4. Shootings in richer areas, stayed longer in the trends.


5. In states with looser gun control, shootings stayed longer in the trends


## Data from Wikipedia

Erlärung welche Daten, wie gescrapt, wie sehen die Daten aus Deskription


```{r}
url <- "https://en.wikipedia.org/wiki/List_of_mass_shootings_in_the_United_States"
t <- read_html(url)
table <- t %>% html_nodes("#mw-content-text > div > table") %>% html_table(trim=T)

table

```

hier Tabellen zusammensetzten

erstes klappt, danach gibt es ein problem mit incompatiblen types. 
Ich glaube wir müssen die buchstaben aus injured rausholen damit wir es in einen integer umändern können

To Do:

- gsub loop --> alle alle nicht zahlen rausziehen
- alle mutaten damit alle integer sein 
- wenn das gemacht alle joinen zu einer großen tabelle
- in excel Extra Variablen hinzufügen
- Datum in Zahlen ändern
- zwei neue variablen, eine zwei Tage vor dem Event und 14 Tage danach
- Description den Namen herausnehmen

```{r}

# Removing unnecessary expressions

for (i in 1:10) {
   table[[i]]$Injured <- gsub("[n 1]", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Injured <- gsub("[n 2]", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Injured <- gsub("[n 3]", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Injured <- gsub("[n 4]", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Injured <- gsub("[n 5]", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Injured <- gsub("[n 6]", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Injured <- gsub("[n 7]", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Injured <- gsub("[n 8]", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Injured <- gsub("[n 9]", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Injured <- gsub("+", "", table[[i]]$Injured, fixed = TRUE)
   table[[i]]$Dead <- gsub("[n 1]", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Dead <- gsub("[n 2]", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Dead <- gsub("[n 3]", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Dead <- gsub("[n 4]", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Dead <- gsub("[n 5]", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Dead <- gsub("[n 6]", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Dead <- gsub("[n 7]", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Dead <- gsub("[n 8]", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Dead <- gsub("[n 9]", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Dead <- gsub("+", "", table[[i]]$Dead, fixed = TRUE)
   table[[i]]$Total <- gsub("+", "", table[[i]]$Total, fixed = TRUE)
}


# Storing Injured, Dead and Total as numerics

for (i in 1:10) {
  as.numeric(as.character(table[[i]]$Injured))
  as.numeric(as.character(table[[i]]$Dead))
  as.numeric(as.character(table[[i]]$Total))
}


#####################################
# Date formatting not working
#dates <- table[[1]]$Date
#betterDates <- as.Date(dates,
#format = "%m %d %Y")

#table[[1]]

#for (i in 1:10) {
  #parse_date_time2("table[[i]]$Date", orders = "mdy")
  #as_date(table[[i]]$Date, tz = NULL, format = NULL)
  #as_date(table[[i]]$Date, origin = lubridate::origin)
  #c(as_date(table[[i]]$Date), as.Date(table[[i]]$Date))
#  date <- as.Date(table[[i]]$Date, format = "%B %d, %Y")
#}

#table[[1]]
####################################################

# Joining all tables to one data frame

newtab <- table[[1]]

for (i in 1:10) {
  newtab <- newtab %>% full_join(table[[i]], by = c("Date", "Location", "Dead", "Injured", "Total", "Description"))
}

newtab

# Works for simple dates, need to think about how we handle timespans --> at the moment converting them gives NAs

str(newtab$Date)

for (i in 1:10) {
   newtab$Date <- gsub(" ", "-", newtab$Date, fixed = TRUE)
   newtab$Date <- gsub(",", "", newtab$Date, fixed = TRUE)
}

newtab


#Deleting the useless part of description --> possibly need to remove year as nobody googles the year when event is happening

newtab$Description <- sub(":.*$", "", newtab$Description)
newtab
```


```{r}
lct <- Sys.getlocale("LC_TIME"); Sys.setlocale("LC_TIME", "C")
newtab[["Date"]] <- as.Date(newtab$Date, format = "%B-%d-%Y")
newtab

newtab$Prior <- newtab$Date - 2
newtab$After <- newtab$Date + 14
newtab

newtab <- na.omit(newtab)


#colnames(newtab)
newtab <- newtab[, c("Date", "Prior", "After", "Location", "Dead", "Injured", "Total", "Description")] 
newtab

newtab$TrendPeriod <- paste(newtab$Prior, newtab$After)
newtab

```

Erwähnen, dass wir nur nach einem Begriff suchen
Search Terms verglichen bei Trends 
Alle Events, die über Tage gehen gedropped
Sophie: 6-10 subben
Hannah: 11-15 

```{r}

newtab$SearchTerm <- gsub("shootout", "shooting", newtab$Description, fixed = TRUE)
newtab

newtab <- newtab[, c("Date", "Prior", "After", "TrendPeriod", "SearchTerm", "Description", "Location", "Dead", "Injured", "Total", "Description")] 
newtab

number <- c("2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")

as.character(number)

for (i in number){
   newtab$SearchTerm <- gsub(i , "", newtab$SearchTerm, fixed = TRUE)
}
newtab

newtab$SearchTerm <- gsub(" at Charlotte", "", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("January ", "", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub(", ", " ", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("shootings", "shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("attack", "shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Shooting of Jemel Roberson", "Jemel Roberson shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Fifth Third Center shooting", "Cincinatti shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Jacksonville Landing shooting", "Jacksonville shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Art All Night shooting", "Trenton shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Copper Canyon Apartment Homes shooting", "Highlands Ranch shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Rancho Tehama Reserve shooting", "Tehama shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Sutherland Springs church shooting", "Sutherland Springs shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Burnette Chapel shooting", "Antioch shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Clovis library shooting", "Clovis shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Little Rock nightclub shooting", "Little Rock shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Bronx-Lebanon Hospital shooting", "Bronx shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("San Francisco UPS shooting", "San Francisco shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Congressional baseball shooting", "Alexandria shooting", newtab$SearchTerm, fixed = TRUE)
newtab$SearchTerm <- gsub("Eaton Township Weis Markets shooting", "Weis Markets shooting", newtab$SearchTerm, fixed = TRUE)


newtab

save(newtab, file="wikishootings.Rda")

```







```{r}
?gtrends
```

In this notebook, we want to explore the search interest in crime related topics in Chicago, IL. In order to narrow our API query to a specific region, DMA codes can be used.

https://help.ooyala.com/video-platform/reference/dma_codes.html

The resulting object is of class `gtrends`, for which the `gtrends` package provides a tailored plotting function.


Gtrends 
--> scraping von mehreren Namen auf einmal

```{r}
shootings <- gtrends(c("Milwaukee shooting", "Grantsville shooting", "El Paso shooting"), geo = "US", time = "2012-01-01 2020-05-07", low_search_volume = T)
plot(shootings)
shootings
```

Versuch eines Loop der einzelne outcomes speichert
```{r}
tab18 <- table[2]
shootnames <- c("Jersey City Shooting", "Naval Air Station Pensacola shooting", "Miramar shootout", "Fresno shooting")

listshooting <- list()
for (i in 1:nrow(newtab)){
    x <- as.vector(newtab$Date[i])
    y <- as.vector(newtab$TrendPeriod[i])
    shooting <- gtrends(keyword = x, geo = "US", time = y, low_search_volume = T)
    iteration <- (1 + length(listshooting))
    listshooting[[iteration]] <- shooting
 }












listshooting <- list()
for (i in newtab$SearchTerm){
    for (k in newtab$TrendPeriod){
      if (nrow(i) == nrow(k)) {
    shooting <- gtrends(keyword = i, geo = "US", time = k, low_search_volume = T)
    print(shooting)
    listshooting <- append(listshooting, shooting)
    }
    }
}

listshooting$interest_over_time

combineshootings <- rbind(listshooting[[1]], listshooting[[8]], listshooting[[15]], listshooting[[22]])
combineshootings

```

Hier dran arbeiten dass ein column ein vektor darstellt und dann in einem Loop genutzt werden kann

```{r}
tab18 <- table[2]
date <- as.vector(c("2019-12-10", "2019-12-6", "2019-12-5", "2019-11-19"))
date <- as.Date(date, "%Y-%m-%d")

pol <- as.vector(tab18['Date'])
class(pol) 

df <- data.frame()
for (i in date){
   df <- print(as.Date('i') - 2)
}
tab18$Date <- as.Date(tab18$Date)

vector <- c()
for(i in 1:ncol(tab18)){
  d <- as.Date("i", format = "%Y-%m-%d")
  vector <- c(vector, d)
}
vector

tab18$Date <- as.Date( as.character(tab18$Date), format='%Y.%m.%d')

tab18$Date <- as.Date(tab18$Date,format='%d.%m.%Y')

tab18

tab18 %>%
   group_by(Deaths) %>%
   mutate(Date=as.Date(Date, format = "%Y.%m.%d"))

mutate(tab18, date= as.Date(Date, format= "%d.%m.%Y"))
```
Information on what is plotted on the y axis can be found here:



```{r}
shootings <- gtrends(c("Milwaukee shooting", "Grantsville shooting", "El Paso shooting", "Sandy Hook shooting"), geo = "US", time = "2012-01-01 2020-05-07", low_search_volume = T)
plot(shootings)
shootings
```


Information on what is plotted on the y axis can be found here:

https://support.google.com/trends/answer/4365533?hl=en

A quick look at the structure of the `res` object.

```{r}
str(shootings)
```

Seems like the first element of this list is a `data.frame` which holds the main results of the API query.

```{r}
shootings$interest_over_time
```

## tidyr

We will use the `tidyr` package to tidy up this data set. In addition, we will need different piping operators from `magrittr`.

```{r}
# install.packages("tidyverse")
library(tidyverse)
library(magrittr)
```

First, we transform the `data.frame` into a `tibble`.

```{r}
shootings_time <- as_tibble(shootings$interest_over_time)
glimpse(shootings)
```



The resulting object is of class `gtrends`, for which the `gtrends` package provides a tailored plotting function.

```{r}
sandy <- gtrends(c("Sandy Hook shooting"), geo = "US", time = "2012-12-12 2012-12-30", low_search_volume = T)
plot(sandy)
sandy
```


Information on what is plotted on the y axis can be found here:

https://support.google.com/trends/answer/4365533?hl=en

A quick look at the structure of the `res` object.

```{r}
str(sandy)
```



```{r}
sandy$interest_over_time
```

## tidyr

We will use the `tidyr` package to tidy up this data set. In addition, we will need different piping operators from `magrittr`.

```{r}
# install.packages("tidyverse")
library(tidyverse)
library(magrittr)
```

First, we transform the `data.frame` into a `tibble`.

```{r}
sandy_time <- as_tibble(sandy$interest_over_time)
glimpse(sandy)
```

